Modelling BCG vaccination in the UK

### 2019-12-17 rmds/08-model-development.Rmd
cleared cache

Parameters distributions were either estimated from the available data, assumed based on common values found in the literature, or based on expert opinion. Parameter distributions were assumed to be normal unless otherwise stated. Where no comparable estimates were found in the literature, and data was not available, a largely uninformative distribution was used, informed by expert opinion. Normal distributions were extrapolated based on the published confidence/credible intervals. All prior distributions were truncated to be greater than or equal to 0 with proportions further truncated to be less than or equal to 1. Prior distributions are first summarised in tables stratified by submodel, with additional details on their derivation given in the following sections. Code for all prior derivations is available online^[https://github.com/seabbs/ModelTBBCGEngland/tree/master/data-raw]. The data sources used to estimate model parameters have been detailed although for the ETS and the LFS more detail is provided elsewhere (Chapter \@ref(data)).

>>>>

Parameters distributions were either estimated from the available data, assumed based on common values found in the literature, or based on expert opinion. Parameter distributions were assumed to be normal unless otherwise stated. Where no comparable estimates were found in the literature, and data was not available, a largely uninformative distribution was used, informed when possible by expert opinion. Normal distributions were extrapolated based on published confidence/credible intervals for prior distributions based on literature sources. All prior distributions were truncated to be greater than or equal to 0 with proportions further truncated to be less than or equal to 1. Prior distributions are first summarised in tables stratified by submodel, with additional details on their derivation given in the subsequent sections. Code for all prior derivations is available online^[https://github.com/seabbs/ModelTBBCGEngland/tree/master/data-raw]. The data sources used to estimate model parameters have been detailed although for the ETS and the LFS more detail is provided elsewhere (Chapter \@ref(data)).
